\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-11-02 slides/gvn-hoist.tex
cost model

\frame{\frametitle{\GVN{}-Hoist: Hoisting Computations from Branches}
  \begin{itemize}
    \item Identifies identical computations in a function
    \item Hoist identical computations to a common dominator
    \item Uses GVN and MemorySSA
    \item Reduces code size
  \end{itemize}
}

\frame{\frametitle{Optimistic \GVN{}-hoist Algorithm}
  \begin{itemize}
  \item DFS number all instructions
  \item Compute value number of scalars, loads, stores, calls
  \item Compute insertion points of each type of instructions
  \item Hoist expressions
  \end{itemize}
}

@@

\frame{\frametitle{\GVN{}-Hoist: Algorithm-hoist expressions}
  \begin{itemize}
  \item Scalars: Just move one of the instrutions to the hoisting point and remove others. Update SSA.
  \item Loads and Stores: Try to make geps available (if not), and then hoist. Update SSA and memory SSA.
  \item Calls: Hoist just like scalars. Update SSA.
  \end{itemize}
}

@@

\frame{\frametitle{Cost models}
  \begin{itemize}
  \item Do not hoist too far
  \item Do not hoist GEPs
  \end{itemize}
}

>>>>

\frame{\frametitle{\GVN{}-Hoist: Hoisting Computations from Branches}
  \begin{itemize}
    \item Identifies identical computations in a function
    \item Hoist identical computations to a common dominator
    \item Reduces code size
    \item Reduces critical path lenth in some cases by exposing more ILP.
  \end{itemize}
}

; TODO: Examples of hoisting

\frame{\frametitle{Optimistic \GVN{}-hoist Algorithm}
  \begin{itemize}
  \item DFS number all instructions
  \item Compute value number of scalars, loads, stores, calls
  \item Compute insertion points of each type of instructions
  \item Hoist expressions
  \item Propagate changes by upating SSA
  \end{itemize}
}

@@

\frame{\frametitle{\GVN{}-Hoist: Algorithm-hoist expressions}
  \begin{itemize}
  \item Scalars: Just move one of the instrutions to the hoisting point and remove others. Update SSA.
  \item Loads and Stores: Try to make geps available (if not), and then hoist. Update SSA and memory SSA.
  \item Calls: Hoist just like scalars. Update SSA.
  \item Set minimum alignment among all the candidates for loads and stores, maximum for allocas.
  \end{itemize}
}

@@

\frame{\frametitle{Cost models}
  \begin{itemize}
  \item Limit the number of Basic Blocks in the path between initial position
    and the hoisting point
  \item Limit the number of instructions between the initial position and the
    beginning of its Basic Block
  \item Do not hoist GEPs
  \item Limit the number of dependent instructions to be hoisted
  \end{itemize}
}
